Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-06-21 ref_response.tex

\subsubsection{Apparent magnitude limits \label{subsubsec:mag_lims}}
As we use photometric, rather than spectroscopic, redshifts for the field galaxies, they do not suffer from spectroscopic incompleteness as the SN hosts do. Instead, the inclusion of any given galaxy in the survey area in the sample is determined simply by whether it is detected above a prescribed threshold in signal-to-noise ratio, i.e. the sample is magnitude limited modulo the cuts described in Section \ref{subsec:cuts}. To determine the apparent magnitude limit for galaxies in each of the optical bands we employ the method of \citet{Johnston2007}, \citet{Teodoro2010}, and \citet{Johnston2012} (hereafter Completeness I, II, III respectively). We use the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ from those studies, which are computed based on absolute magnitude (distance modulus). Each galaxy is ranked by its absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude). For a galaxy of apparent magnitude $m < m_{\mathrm{lim, trial}}$ observed in a survey complete to magnitude $m_{\mathrm{lim, true}}$ where  $m_{\mathrm{lim, trial}} \leq m_{\mathrm{lim, true}}$, the expectation value of the rank is 0.5. However, if a trial limiting magnitude $m_{\mathrm{lim, trial}} \geq m_{\mathrm{lim, true}}$, there will be a lack of observed faint objects, such that the expectation value of the rank drops.

Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ are stable and flat as a function of apparent magnitude up until the magnitude limit, where they drop sharply. The DES deep stacks present a more challenging case. They cover a wide area and are compiled from tens of separate CCDs, each with its own detection efficiency. Moreover, galaxy redshifts have been estimated using photometry only, and $K$-corrections performed using an imperfect template fit, potentially leading to large systematic and statistical fluctuations in absolute magnitudes and distance moduli. To reduce the inhomogeneity while still including  large sample of objects, we limit our sample to include only data from one deep (SN-X3) field. Fig. \ref{fig:completeness} shows the values of $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$. The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey. The shape at brighter $m_{\mathrm{lim, trial}}$ is likely caused by incompleteness at the bright end: due to the small sky area, we simply do not probe enough volume to sample the bright end of the galaxy luminosity function well enough for the statistics to be robust. To approximate an efficiency function, we fit the peak of the statistics with a polynomial function, and then normalise by the maximum and minimum values. We then interpolate between the peak and the faint-magnitude floor to find the 50\% completeness limit at the point where the normalised value of the test statistic is 0.5. These values are consistent with the value at which 50\% of the true sources are detected but have the advantage of being derived from the data without a simulation that is based on assumptions and thus susceptible to bias.
\subsubsection{$V_{\mathrm{max}}$ correction \label{subsubsec:vmax_corr}}

@@

The rate of SNe Ia per galaxy as a function of stellar mass is shown in Fig. \ref{fig:rate_raw}. The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function in log space, which corresponds to a power law. To find the slope and intercept that best describe the data we use Bayesian inference. To sample the posterior we use the enhanced no-U-turn Sampler (NUTS) algorithm \citep{Betancourt2017}, which is a variant of Hamiltonian Monte-Carlo (HMC), implemented in the Stan programming language \citep{Carpenter2017}. We describe the fitting procedure in full detail in Appendix \ref{appendix:linear_fits}. We measure a slope of $0.63\pm0.02$, which is consistent with the value found in weakly star-forming galaxies in the Supernova Legacy Survey by \citet{Sullivan2006}, but also in passive galaxies in SDSS by \citet{Smith2012}, and in all galaxies in the Lick Observatory Supernova Search (LOSS) by \citet{Li2011a}. Our measured slope is also consistent with that measured in the low-redshift All-Sky Automated Survey for Supernova (ASAS-SN) Bright Supernova Catalogues \citep{Brown2019}, which extends to galaxies with stellar mass as low as $10^7$~M$_{\odot}$.

>>>>

\subsubsection{Apparent magnitude limits \label{subsubsec:mag_lims}}
As we use photometric, rather than spectroscopic, redshifts for the field galaxies, they do not suffer from spectroscopic incompleteness as the SN hosts do. Instead, the inclusion of any given galaxy in the survey area in the sample is determined simply by whether it is detected above a prescribed threshold in signal-to-noise ratio, i.e. the sample is magnitude limited modulo the cuts described in Section \ref{subsec:cuts}. To determine the apparent magnitude limit for galaxies in each of the optical bands we employ the method of \citet{Johnston2007}, \citet{Teodoro2010}, and \citet{Johnston2012} (hereafter Completeness I, II, III respectively). These works provide two complimentary statistics in order to find the limiting magnitude based on ranking of galaxies' absolute magnitudes in a given band $M$ and distance moduli $Z$, named  $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$, respectively. Galaxies are first placed in the $M-Z$ plane, which is limited to distance moduli that correspond to the redshift cuts $0.2 <z<0.6$ introduced in Section \ref{subsec:incompleteness_SNe}. Each galaxy in the survey is ranked by its $Z$ ($M$) compared to all other galaxies that fall within a slice of width $\delta M$ ($\delta Z$) -- we find that $\delta M = \delta Z = 0.02$~mag provides the best balance between high sampling resolution and an adequate number of galaxies within each slice. We then iteratively test different trial limiting apparent magnitudes $m_{\mathrm{lim, trial}}$. For a galaxy of apparent magnitude $m < m_{\mathrm{lim, trial}}$ observed in a survey complete to magnitude $m_{\mathrm{lim, true}}$ where  $m_{\mathrm{lim, trial}} \leq m_{\mathrm{lim, true}}$, the expectation value of the rank for a random is 0.5. However, if a trial limiting magnitude $m_{\mathrm{lim, trial}} \geq m_{\mathrm{lim, true}}$, there will be a lack of observed faint objects, such that the expectation value of the rank drops.

Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ are stable and flat as a function of apparent magnitude up until the magnitude limit, where they drop sharply. Fig. \ref{fig:completeness} shows the values of $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ in the DES X3 field. The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey, contrary to the sharp drop in an ideal survey. The shape at brighter $m_{\mathrm{lim, trial}}$ is likely caused by incompleteness at the bright end: due to the small sky area, we simply do not probe enough volume to sample the bright end of the galaxy luminosity function well enough for the statistics to be robust.

To approximate an efficiency function, we fit the peak of the statistics with a polynomial function, and then normalise by the maximum and minimum values. We then interpolate between the peak and the faint-magnitude floor to find the 50\% completeness limit at the point where the normalised value of the test statistic is 0.5. These values are consistent with the value at which 50\% of the true sources are detected but have the advantage of being derived from the data without a simulation that is based on assumptions and thus susceptible to bias. Our final limiting magnitude for each band is the mean of that found from each of  $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$.
\subsubsection{$V_{\mathrm{max}}$ correction \label{subsubsec:vmax_corr}}

@@

The rate of SNe Ia per galaxy as a function of stellar mass is shown in Fig. \ref{fig:rate_raw}. The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function in log space, which corresponds to a power law. To find the slope and intercept that best describe the data we use Bayesian inference. To sample the posterior we use the enhanced no-U-turn Sampler (NUTS) algorithm \citep{Betancourt2017}, which is a variant of Hamiltonian Monte-Carlo (HMC), implemented in the Stan programming language \citep{Carpenter2017}. We describe the fitting procedure in full detail in Appendix \ref{appendix:linear_fits}. We measure a slope of $0.63\pm0.02$, which is consistent with the value found in weakly star-forming galaxies in the Supernova Legacy Survey by \citet{Sullivan2006}, but also in passive galaxies in SDSS by \citet{Smith2012}, and in all galaxies in the Lick Observatory Supernova Search (LOSS) by \citet{Li2011a}. Our slope is also consistent with that measured in the low-redshift All-Sky Automated Survey for Supernova (ASAS-SN) Bright Supernova Catalogues \citep{Brown2019}, which extends to galaxies with stellar mass as low as $10^7$~M$_{\odot}$.
